\chapter{Skills Analysis} % Main chapter title

\label{Chapter3} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{Chapter3}

\lhead{Chapter 3. \emph{Skills Analysis}} % Change X to a consecutive number; this is for the header on each page - perhaps a shortened title

In this chapter I describe, analyse and demonstrate the knowledge and skills I have developed and gained throughout my university education
(see courses in Table~\ref{tbl:courses})
and work experiences in industry
(see placements in Figure~\ref{timeline}).
This has been done in line with the learning outcomes (LOs) as stipulated by the Engineering Council for the university programmes that the council accredits (see Appendix~\ref{App:ECLOs}), as well as the Graduate Attributes of Heriot-Watt University (see Appendix~\ref{App:HWgrad}).


% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
% \usepackage{multirow}
\begin{table}[htbp]
	\caption{The courses I took for MEng Architectural Engineering}
	\label{tbl:courses}
	\centering
	\begin{tabular}{@{}lll@{}}
		\toprule
		\textbf{} & \textbf{Code} & \textbf{Course Title} \\ \midrule
		\multirow{8}{*}{\textbf{Year 1}} & D37TA & Construction Technology 1 \\
		& D17HH & History of the Built Environment \\
		& D17DE & Introduction to Design \\
		& F17XA & Mathematics for Engineers and Scientists 1 \\
		& D18BT & Building Services Technology \\
		& D27MB & Mechanics B \\
		& D47IE & Introduction to the Environment \\
		& F17XB & Mathematics for Engineers and Scientists 2 \\ \midrule
		\multirow{8}{*}{\textbf{Year 2}} & D18PA & Design Project A \\
		& D38TA & Construction Technology 2 \\
		& D18AB & Acoustics and Architectural Design \\
		& D28HA & Hydraulics and Hydrology A* \\
		& D17BG & Environment and Behaviour \\
		& F78SC & Statistics for Science \\
		& D18EP & Energy Principles and Applications \\
		& D18DP & Design Project B* \\ \midrule
		\multirow{8}{*}{\textbf{Year 3}} & D19CX & Critical Architectural Studies \\
		& D19EL & Electrical and Lighting Services for Buildings \\
		& D19SO & Design Software Applications \\
		& D39PZ & Procurement and Contracts \\
		& D19EB & Energy and Buildings \\
		& D19TP & Thermal Performance Studies \\
		& D19DI & Design Issues \\
		& D38FM & Facilities Management Principles \\ \midrule
		\multirow{6}{*}{\textbf{Year 4}} & D10YD/F & Design Project (AE) (S1/S2) \\
		& D10ZA/B & Dissertation (AE) (S1/S2) \\
		& D10LP & Laboratory Project \\
		& D10IE & Inclusive and Safe Environments \\
		& D10IS & Sustainable and Intelligent Buildings \\
		& D30IC & Innovation in Construction Practice \\ \midrule
		\multirow{7}{*}{\textbf{Year 5}} & D11PJ & Industrial Project \\
		& D11CA & Climate Change, Sustainability and Adaptation* \\
		& D21WC & Water Supply and Drainage for Buildings* \\
		& \textcolor{gray}{D11AF} & \textcolor{gray}{Architectural Acoustics} \\
		& \textcolor{gray}{D11DC} & \textcolor{gray}{Design of Low Carbon Buildings} \\
		& \textcolor{gray}{D11TH} & \textcolor{gray}{Thermofluids} \\
		& \textcolor{gray}{--} & \textcolor{gray}{\textit{To be determined}*} \\ \bottomrule
		\multicolumn{3}{l}{\textit{*Optional courses}} \\
		\multicolumn{3}{l}{\textcolor{gray}{\textit{Courses to be taken in 2019 are displayed in grey}}} \\
	\end{tabular}
\end{table}


I am studying an integrated Master of Engineering (MEng) degree in Architectural Engineering at Heriot-Watt University.
The degree is accredited by the Chartered Institution of Building Services Engineers (CIBSE), which is a licensed institution of the Engineering Council.
This means that when somebody joins CIBSE, they will also be registered as a Chartered Engineer (CEng), Incorporated Engineer (IEng) or Engineering Technician (EngTech) when they have reached the appropriate level of qualification and professional skill \citep{whyjoinCIBSE}.

The LOs of the degree programmes accredited by the Engineering Council are divided up into six categories:
\begin{itemize}
    \item Science and mathematics (SM)
    \item Engineering analysis (EA)
    \item Design (D)
    \item Economic, legal, social, ethical and environmental context (EL)
    \item Engineering practice (P)
    \item Additional general skills (G)
\end{itemize}
Each category has a list of LOs which are depicted by the category abbreviation (e.g. SM) and a number (e.g. 1); examples of LOs are SM1, EA2 and D3.
Most of these LOs are divided into, at the most, three incrementally increasing attainment levels which are depicted by the letters ``i", ``b" or ``m", e.g. SM1i, SM1b and SM1m.
From the \textit{UK Standard for Professional Engineering Competence} \citep{EngineeringCouncil2014}, 
I have been able to deduce that:
\begin{itemize}
    \item \textbf{``i"} represents the LOs of Bachelors Degrees and Bachelors (Honours) Degrees accredited for IEng registration.
    \item \textbf{``b"} represents the LOs of Bachelors (Honours) Degrees accredited as partially meeting the educational requirement for CEng registration.
    \item \textbf{``m"} represents the LOs of integrated Masters (MEng) degrees accredited for CEng registration.
\end{itemize}

Some LOs are only divided into two attainment levels, one of which is not depicted by a letter ``i", ``b" or ``m", e.g. EA2i and EA2.
In such cases, the LO with the letter ``i", ``b" or ``m" applies to the corresponding attainment level and the LO without the letter applies to all the other attainment levels.
In the example of EA2i and EA2, EA2 applies to both attainment levels ``b" and ``m".

Other LOs, however, are not depicted by any of the letters ``i", ``b" or ``m", e.g. D6.
These LOs therefore apply to all three of the attainment levels.\footnote{
For consistency, I have amended seven of the LO abbreviations given to us in the D11PJ Course Handbook.
The LOs D3, EL3, EL6, P2, P11 and G3 were respectively changed to D3i, EL3b, EL6b, P2b, P11b and G3b.
Since the LOs P4 and P4m are identical, I have merged them to the single LO P4.
These amendments were done so that the naming conventions described above always apply.}

The approach of my skills analysis in this chapter is competency-based.
I have grouped the attainment levels of the LOs, such as SM1(i, b, m) and EA2(i, -), where the dash ``-" depicts the LO without ``i", ``b" or ``m" as an ending letter.
%\hl{Continue with the method I have used to demonstrate my achievement (or not) of the LOs, e.g. boxes for course codes.}

The \textit{UK Standard for Professional Engineering Competence} uses the following terms and their definitions, which will also apply within this document \citep{EngineeringCouncil2014}:
%\hl{Re-arranged extract from AHEP 3rd edition}:
\begin{itemize}
    \item \textbf{Awareness} is general familiarity, albeit bounded by the needs of the specific discipline

    \item \textbf{Knowledge} is information that can be recalled

    \item \textbf{Understanding} is the capacity to use concepts creatively, for example, in problem solving, design, explanations and diagnosis

    \item \textbf{Skills} are acquired and learned attributes that can be applied almost automatically

    \item \textbf{Know-how} is the ability to apply learned knowledge and skills to perform operations intuitively, efficiently and correctly

    \item \textbf{Complex} implies engineering problems, artefacts or systems that involve dealing simultaneously with a sizeable number of factors that interact and require deep understanding, including knowledge at the forefront of the discipline, to analyse or deal with

\end{itemize}


\begin{comment}
% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
% \usepackage{multirow}
\begin{table}[h]
\caption{The courses I took towards my MEng degree in Architectural Engineering at Heriot-Watt University (include course codes? transpose table!)}
\label{courses}
	\begin{tabular}{@{}lp{8cm}p{7.5cm}@{}}
		\toprule
		& Semester 1 & Semester 2 \\ \midrule
		\multirow{4}{*}{\rot{Year 1}} & \textbullet \hspace{0.5ex}Construction Technology 1 & \textbullet \hspace{0.5ex}Building Services Technology \\
		& \textbullet \hspace{0.5ex}History of the Built Environment & \textbullet \hspace{0.5ex}Mechanics B \\
		& \textbullet \hspace{0.5ex}Introduction to Design & \textbullet \hspace{0.5ex}Introduction to the Environment \\
		& \textbullet \hspace{0.5ex}Mathematics for Engineers and Scientists 1 & \textbullet \hspace{0.5ex}Mathematics for Engineers and Scientists 2 \\ \midrule
		\multirow{4}{*}{\rot{Year 2}} & \textbullet \hspace{0.5ex}Design Project A & \textbullet \hspace{0.5ex}Environment and Behaviour \\
		& \textbullet \hspace{0.5ex}Construction Technology 2 & \textbullet \hspace{0.5ex}Statistics for Science \\
		& \textbullet \hspace{0.5ex}Acoustics and Architectural Design & \textbullet \hspace{0.5ex}Energy Principles and Applications \\
		& \textbullet \hspace{0.5ex}\textit{Hydraulics \& Hydrology A} & \textbullet \hspace{0.5ex}\textit{Design Project B} \\ \midrule
		\multirow{4}{*}{\rot{Year 3}} & \textbullet \hspace{0.5ex}Critical Architectural Studies & \textbullet \hspace{0.5ex}Energy and Buildings \\ 
		& \textbullet \hspace{0.5ex}Procurement and Contracts & \textbullet \hspace{0.5ex}Thermal Performance Studies \\
		& \textbullet \hspace{0.5ex}Design Software Applications & \textbullet \hspace{0.5ex}Design Issues \\
		& \textbullet \hspace{0.5ex}Electrical and Lighting Services for Buildings & \textbullet \hspace{0.5ex}Facilities Management Principles \\ \midrule
		\multirow{4}{*}{\rot{Year 4}} & \textbullet \hspace{0.5ex}Design Project (S1) & \textbullet \hspace{0.5ex}Design Project (S2) \\
		& \textbullet \hspace{0.5ex}Dissertation (S1) & \textbullet \hspace{0.5ex}Dissertation (S2) \\
		& \textbullet \hspace{0.5ex}Laboratory Project & \textbullet \hspace{0.5ex}Sustainable and Intelligent Buildings \\
		& \textbullet \hspace{0.5ex}Inclusive and Safe Environments & \textbullet \hspace{0.5ex}Innovation in Construction Practice \\ \midrule
		\multirow{4}{*}{\rot{Year 5}} & \textbullet \hspace{0.5ex}Industrial Project & \textbullet \hspace{0.5ex}Architectural Acoustics \\
		& \textbullet \hspace{0.5ex}\textit{Water Supply \& Drainage for Buildings} & \textbullet \hspace{0.5ex}Design of Low Carbon Buildings \\
		& \textbullet \hspace{0.5ex}\textit{Climate Change, Sustainability \& Adaptation} & \textbullet \hspace{0.5ex}Thermofluids \\
		&  & \textbullet \hspace{0.5ex}\textit{OPTIONAL} \\ \bottomrule
	\end{tabular}
\end{table}
\end{comment}



\begin{comment}
\begin{tcolorbox}[width=\textwidth/3,leftrule=3mm,enhanced,attach boxed title to top center={yshift=-3mm,yshifttext=-1mm},
colback=blue!5!white,colframe=blue!75!black,colbacktitle=red!80!black,
title=My title,fonttitle=\bfseries,
boxed title style={size=small,colframe=red!50!black} ]
This box uses a \textit{boxed title}. The box of the title can
be formatted independently from the main box.
\end{tcolorbox}
\end{comment}


%----------------------------------------------------------------------------------------
%	SECTIONS
%----------------------------------------------------------------------------------------

\input{Sections/031-SM.tex}
\input{Sections/032-EA.tex}
\input{Sections/033-D.tex}
\input{Sections/034-EL.tex}
\input{Sections/035-P.tex}
\input{Sections/036-G.tex}

